### 2017-11-22 Risk analysis/Text/Layout/Layout/chapter1.tex
Kind of finished all main parts

Bayesian decision theory and the related concepts of expected loss and loss functions have found increasingly common application in several economic sectors and fields of research, such as medicine \citep{ashby2000evidence, ashby2006bayesian, moye2006statistical} and machine learning \citep{barber2012bayesian, theodoridis2015machine}. Probabilistic approaches to decision-making have also become prevalent in the sector of hydrocarbon exploration and production (SOURCE). However, the methods here a mainly limited on (p10-p90, decision trees).......(see BRATVOLD)???\\

@@

This work builds upon their concept, exploring the potential significance their findings might have in the context of decision-making. Bayesian decision-theory is to be included in the step of model evaluation. This is achieved by assigning an economic meaning to the structural model and designing a case-specific custom loss functions to find decisions which are optimal related to the state of knowledge and the preferences of actors with different risk-affinities. More specifically, the models are designed to represent potential petroleum systems. Consequently, the development of algorithms for automatic hydrocarbon trap recognition and volume calculation represent a central part of this work.\\
The main hypothesis of this work is that Bayesian inference and resulting changes in uncertainties in a geological setting have a significant effect on related value estimation and decision-making. It is furthermore postulated that loss functions can be customized to appropriately represent preferences of actors in the hydrocarbon sector and moreover illustrate the nature of decisions such actor's might make depending on their individual attitudes towards risk and in the face of different types of uncertainties. Changes in their respective decisions are treated as a suitable measure to assess the effect of updating model parameters with new geological information.

>>>>

Bayesian decision theory and the related concepts of expected loss and loss functions have found increasingly common application in several economic sectors and fields of research, such as medicine \citep{ashby2000evidence, ashby2006bayesian, moye2006statistical} and machine learning \citep{barber2012bayesian, theodoridis2015machine}. Probabilistic approaches to decision-making have also become prevalent in hydrocarbon exploration and production \citep{murtha1997monte, mudford2000valuing,bratvold2010making}. However, in this sector, the methods are mainly limited to conducting simple Monte Carlo simulations and results are often interpreted viewing only percentiles and single values such as the mean. Bayesian inference and Markov chain Monte Carlo methods have only recently received more attention by researchers in this field (see \citet{wadsley2005markov}, \citet{ma2006multistage} and \citet{liu2010continuous}).\\

@@

This work builds upon their concept, exploring the potential significance their findings might have in the context of decision-making. For this, we include Bayesian decision theory in the step of model evaluation. This is achieved by assigning an economic meaning to the structural model and designing a case-specific custom loss function to find decisions which are optimal related to the state of knowledge and the preferences of actors with different risk-affinities. More specifically, the models are designed to represent potential petroleum systems. Consequently, the development of algorithms for automatic hydrocarbon trap recognition and volume calculation represent a central part of this work.\\
The main hypothesis of this work is that Bayesian inference and resulting changes in uncertainties in a geological setting have a significant effect on reservoir value estimation and decision-making. We furthermore postulate that loss functions can be customized to appropriately represent preferences of actors in the hydrocarbon sector and moreover illustrate the nature of decisions such actor's might make depending on their individual attitudes towards risk and in the face of different types of uncertainties. Changes in their respective decisions are treated as a suitable measure to assess the effect of updating model parameters with new geological information.

### 2017-11-22 Risk analysis/Text/Layout/Layout/chapter4_discussion.tex
Kind of finished all main parts

	From a decision-making perspective, these scenarios might be interpreted as different decision options. In a case of distinct bimodality as seen in the prior of the 3D model, two main options would be given: (1) to not take any action, or (2) to allocate resources according to an estimated value within the positive mode. However, most often, low probabilities for the values between these two opposite options remain. Especially considering the use of loss functions which lead to best estimates located in these areas of low probability, it is debatable, how these ranges should be treated. A possibility could be to subdivide the value probability distribution accordingly into regions. Considering respective integral probabilities for each such section and by introducing a critical integral probability as a threshold, it could be determined whether such a subregion is to be considered an actual option for decision-making or not. If a Bayes action is located outside of such a decision option, it could be automatically assigned to the closest region of sufficient integral probability. This approach should be easily applicable as an extension to our custom loss function. Furthermore, it could serve to build a bridge between this continuous loss function method and discrete approaches to decision-making, such as decision trees. In real cases, normally only a limited number of options is given. In the context of hydrocarbon exploration and production, this would relate to fixed magnitudes of resource allocation, such as a certain number of required drilling wells or the size of a production platform. A discretization of decision subregions in a probability distribution could thus also be based on previously defined actual options.\\			
	DRAW COMPARISON TO SIMPLE MCS AND DISCRETIZED DECISION THEORY IN HYDROCARBON E\&P HERE!\\	

>>>>

	From a decision-making perspective, these scenarios might be interpreted as different decision options. In a case of distinct bimodality as seen in the prior of the 3D model, two main options would be given: (1) to not take any action, or (2) to allocate resources according to an estimated value within the positive mode. However, most often, low probabilities for the values between these two opposite options remain. Especially considering the use of loss functions which lead to best estimates located in these areas of low probability, it is debatable, how these ranges should be treated. A possibility could be to subdivide the value probability distribution accordingly into regions. Considering respective integral probabilities for each such section and by introducing a critical integral probability as a threshold, it could be determined whether such a subregion is to be considered an actual option for decision-making or not. If a Bayes action is located outside of such a decision option, it could be automatically assigned to the closest region of sufficient integral probability. This approach should be easily applicable as an extension to our custom loss function. Furthermore, it could serve to build a bridge between this continuous loss function method and discrete approaches to structuring decision problems, such as decision trees. In real cases, normally only a limited number of options is given. In the context of hydrocarbon exploration and production, this would relate to fixed magnitudes of resource allocation, such as a certain number of required drilling wells or the size of a production platform. A discretization of decision subregions in a probability distribution could thus also be based on previously defined actual options.\\			
	In remains to be argued, to what extent our methodology and findings contribute regarding practical applications in hydrocarbon exploration and production. Monte Carlo simulation for reservoir estimation and risk assessment have become common in this sector and are often used in combination with decision trees to make decisions (see \citet{murtha1997monte}, \citet{mudford2000valuing} and \citet{bratvold2010making}). However, it seems to us that distributions resulting from probabilistic modeling are mostly only considered to attain best estimates in the form of means. Most likely and extreme outcomes are identified as percentiles, typically P50 (the median), P10 and P90. We believe that this practice does not harness the full potential of such a probabilistic distribution and that much of the inherent information potential is discarded. Contrary to that, customized loss functions as a Bayesian method, take into account the full probability distribution and enable the inclusion of various conditions in the process of finding an optimal estimate. While used in statistical decision theory and other scientific fields, loss functions have, to the best of our knowledge, found no significant application in the field of petroleum exploration and production. Thus, we intend to provide a new perspective with our methodology. \citet{murtha1997monte} emphasized that Monte Carlo simulation does not make decisions, it merely prepares for it. We believe that loss functions have the potential to go one step further. A hypothetical ideal loss function would consider all conditions in an economic environment, as well as perfectly represent preferences and goals of an actor and consequently be able to automatically find an optimal decision. While this is obviously unrealistic, we presume that an elaborate loss function might at least provide a very good preliminary decision recommendation. It might furthermore weight \\
	More recently, Bayesian inference and MCMC methods were applied for OOIP estimation and forecasting of reservoir productivity by \citet{wadsley2005markov}, \citet{ma2006multistage} and \citet{liu2010continuous}. However, their research focused on simulations based on history matching for already producing fields. Our approach of applying Bayesian inference for structural geological modeling and volumetric reservoir calculations is intended to support decision-making in the earliest stages of a reservoir, when it has to be decided whether a project should be developed or not. Nevertheless, in was shown in the work by \citet{wadsley2005markov} that early volumetric OOIP estimates can be combined with later calculations from production data via MCMC methods. This is an area where our methods could possibly be integrated.\\
	\citet{bratvold2010making} highlighted the potential to use Monte Carlo simulation to identify, via sensitivity analysis, which uncertainties have the greatest impact on  decisions. This was virtually achieved by performing several cases of Bayesian inference in our work, as we recognized primarily the importance of seal reliability.\\		
